R Notebook

### 2018-10-10 analysis/final_analysis.Rmd
analysis update

ggsave('../../pragmatics_of_perspective_taking_tex/pnas_format/figures/predictiveScatter.pdf',
       height = 5, width = 9)
```

```{r}
ggplot(to.plot, aes(x = ego_mean, y = emp_mean)) +
  geom_point() +#(stat = 'identity', position = dodge) +
  geom_errorbar(aes(ymin = emp_lower, ymax = emp_upper), width = 0) +
  #geom_errorbarh(aes(xmin = ego_lower, xmax = ego_upper), width = 0) +
  geom_smooth(method = 'lm') +
  theme_few() +
  theme(aspect.ratio = 1, text = element_text(size=20)) +
  xlab('predicted # features')+
  ylab('empirical # features') 
ggsave('../../pragmatics_of_perspective_taking_tex/pnas_format/figures/egocentricScatter.pdf',
       height = 5, width = 9)
```

>>>>

ggsave('../../pragmatics_of_perspective_taking_tex/cognition_format/figures/predictiveScatter.pdf',
       useDingbats=FALSE )
```

```{r}
ggplot(to.plot, aes(x = ego_mean, y = emp_mean)) +
  geom_point() +#(stat = 'identity', position = dodge) +
  geom_errorbar(aes(ymin = emp_lower, ymax = emp_upper), width = 0) +
  #geom_errorbarh(aes(xmin = ego_lower, xmax = ego_upper), width = 0) +
  geom_smooth(method = 'lm') +
  theme_few() +
  theme(aspect.ratio = 1, text = element_text(size=20)) +
  xlab('predicted # features')+
  ylab('empirical # features') 
ggsave('../../pragmatics_of_perspective_taking_tex/cognition_format/figures/egocentricScatter.pdf',
       useDingbats=FALSE)
       #height = 5, width = 9)
```
